Illustrating Model Properties

### 2024-06-20 model.qmd
add scenarios for more risk computations

fig, ax = plt.subplots()
ax.set_xlim(0., 15.)

@@

scenario = Scenario(
  t_stages=["early"],
  midext=False,
  diagnosis={
    "ipsi": {"CT": all_false},
    "contra": {"CT": all_false},
  },
  involvement={"contra": {"II": True}},
)
contents.append(Histogram.from_hdf5(
  filename=paths.model_dir / "full" / "risks.hdf5",
  dataname=scenario.md5_hash("risks"),
  color=COLORS["green"],
  label="early, lateralized; N0",
))

scenario = Scenario(
  t_stages=["late"],
  midext=False,
  diagnosis={
    "ipsi": {"CT": {"III": True}},
    "contra": {"CT": all_false},
  },
  involvement={"contra": {"II": True}},
)
contents.append(Histogram.from_hdf5(
  filename=paths.model_dir / "full" / "risks.hdf5",
  dataname=scenario.md5_hash("risks"),
  color=COLORS["blue"],
  label="advanced, lateralized; ipsi LNL III",
))

scenario = Scenario(
  t_stages=["early"],
  midext=True,
  diagnosis={
    "ipsi": {"CT": all_false},
    "contra": {"CT": all_false},
  },
  involvement={"contra": {"II": True}},
)
contents.append(Histogram.from_hdf5(
  filename=paths.model_dir / "full" / "risks.hdf5",
  dataname=scenario.md5_hash("risks"),
  color=COLORS["orange"],
  label="early, midline extension; N0",
))

scenario = Scenario(
  t_stages=["late"],
  midext=True,
  diagnosis={
    "ipsi": {"CT": {"III": True}},
    "contra": {"CT": all_false},
  },
  involvement={"contra": {"II": True}},
)
contents.append(Histogram.from_hdf5(
  filename=paths.model_dir / "full" / "risks.hdf5",
  dataname=scenario.md5_hash("risks"),
  color=COLORS["red"],
  label="advanced, midline extension; ipsi LNL III",
))

draw(ax, contents, xlims=(0., 15.))
ax.legend(labelspacing=0.3)
ax.set_xlabel("risk [%]")
ax.set_yticks([])
ax.set_title("Predicted Risk of Contralateral LNL II Involvement\nfor Selected Diagnosis Scenarios")

>>>>

nrows, ncols = 1, 3
plt.rcParams.update(shared.get_fontsizes())
plt.rcParams.update(shared.get_figsizes(
  nrows=nrows,
  ncols=ncols,
  width=17,
  aspect_ratio=1.3,
))

fig, ax = plt.subplots(nrows=nrows, ncols=ncols)

@@

# contra LNL II
scenario = Scenario(
  t_stages=["early"],
  midext=False,
  diagnosis={
    "ipsi": {"CT": all_false},
    "contra": {"CT": all_false},
  },
  involvement={"contra": {"II": True}},
)
contents.append(Histogram.from_hdf5(
  filename=paths.model_dir / "full" / "risks.hdf5",
  dataname=scenario.md5_hash("risks"),
  color=COLORS["green"],
  label="early, lateralized; N0",
))

scenario = Scenario(
  t_stages=["late"],
  midext=False,
  diagnosis={
    "ipsi": {"CT": {"III": True}},
    "contra": {"CT": all_false},
  },
  involvement={"contra": {"II": True}},
)
contents.append(Histogram.from_hdf5(
  filename=paths.model_dir / "full" / "risks.hdf5",
  dataname=scenario.md5_hash("risks"),
  color=COLORS["blue"],
  label="adv., lateralized; ipsi LNL III",
))

scenario = Scenario(
  t_stages=["early"],
  midext=True,
  diagnosis={
    "ipsi": {"CT": all_false},
    "contra": {"CT": all_false},
  },
  involvement={"contra": {"II": True}},
)
contents.append(Histogram.from_hdf5(
  filename=paths.model_dir / "full" / "risks.hdf5",
  dataname=scenario.md5_hash("risks"),
  color=COLORS["orange"],
  label="early, mid. ext.; N0",
))

scenario = Scenario(
  t_stages=["late"],
  midext=True,
  diagnosis={
    "ipsi": {"CT": {"III": True}},
    "contra": {"CT": all_false},
  },
  involvement={"contra": {"II": True}},
)
contents.append(Histogram.from_hdf5(
  filename=paths.model_dir / "full" / "risks.hdf5",
  dataname=scenario.md5_hash("risks"),
  color=COLORS["red"],
  label="adv., mid. ext.; ipsi LNL III",
))

draw(ax[0], contents, xlims=(0., 15.))
ax[0].legend(labelspacing=0.1)
ax[0].set_xlabel("risk [%]")
ax[0].set_yticks([])
ax[0].set_xticks(np.linspace(0, 15, 6))
ax[0].set_title("Contralateral LNL II")

# contra LNL III
contents = []

ax[1].set_yticks([])
ax[1].set_xticks(np.linspace(0, 15, 6))

ax[2].set_yticks([])
ax[2].set_xticks(np.linspace(0, 15, 6))
